Getting Started with the Graded Response Model (GRM): A gentle introduction and tutorial in R

### 2023-11-15 draft_paper.qmd
first attempt rendering the Quarto file (manuscript draft)

```{r, echo=F, include=F}
#| label: setup
#| install.packages("tidyverse", "psych", "devtools", "mirt", "caret", dependencies=TRUE) 
#| INFO: Remove the hashtag before install.package() to start installing packages (only if you have not had them installed) ##

#| devtools::install_github("masurp/ggmirt")

#| Now, we activate the package:
library(tidyverse); library(psych); library(mirt); library(ggmirt); library(caret)

>>>>

```{r, echo=F, include=F}
#| label: setup
# install.packages("tidyverse", "psych", "devtools", "mirt", "caret", dependencies=TRUE) 
# INFO: Remove the hashtag before install.package() to start installing packages (only if you have not had them installed)
# devtools::install_github("masurp/ggmirt")
# Now, we activate the package:
library(tidyverse); library(psych); library(mirt); library(ggmirt); library(caret)
